### 2014-02-13 classicthesis/BenchmarkResults.tex
yahoo results + bibliography

\section{Results}
Figure \ref{fig:yahoo_results} shows the top five participants in the Yahoo! Learning to Rank Challenge in terms of ERR score.
\begin{table}
\begin{tabular}{l|p{6.3cm}|l}
 & Authors & ERR \\
 \hline 
1 & Burges et al (Microsoft Research) & 0.46861 \\ 
2 & Gottschalk (Activision Blizzard) \& Vogel (Data Mining Solutions) & 0.46786 \\ 
3 & Parakhin (Microsoft) & 0.46695 \\ 
4 & Pavlov \& Brunk (Yandex Labs) & 0.46678 \\ 
5 & Sorokina (Yandex Labs) & 0.46616 \\ 
\end{tabular}
\caption{Final standings of the Yahoo! Learning to Rank Challenge, as presented in the challenge overview paper\cite{Chapelle2011a}}
\label{fig:yahoo_results}
\end{table}
\chapter{Yandex Internet Mathematics competition}
\section{Benchmark characteristics}
\section{Results}
\chapter{LETOR}
\section{Benchmark characteristics}
\section{Results}
\chapter{MSLR-WEB30k}
Contrary to the Yahoo! Learning to Rank Challenge dataset, the MSLR-WEB30k provides detailed feature descriptions. The MSLR-WEB30k dataset however contains no proprietary features but only features that are commonly used in the research community.
\section{Benchmark characteristics}
\section{Results}

>>>>

\section{Results}
Figure \ref{fig:yahoo_results} shows the top five participants in the Yahoo! Learning to Rank Challenge in terms of ERR score. The top five participants all used decision trees and ensemble methods. Burges et al\cite{Burges2011} created a linear combination ensemble of eight LambdaMART\cite{Burges2010}, two LambdaRank and two Logistic Regression models. Gottschalk and Vogel used a combination of RandomForest models and \ac{GBDT} models. Pavlov and Brunk used a regression based model using the BagBoo\cite{Pavlov2010} ensemble technique, which combines bagging and boosting. Sorokina used a similar combination of bagging and boosting that is called Additive Groves\cite{Sorokina2007}.\\

\begin{table}
\begin{tabular}{l|p{6.3cm}|l}
 & Authors & ERR \\
 \hline 
1 & Burges et al (Microsoft Research) & 0.46861 \\ 
2 & Gottschalk (Activision Blizzard) \& Vogel (Data Mining Solutions) & 0.46786 \\ 
3 & Parakhin (Microsoft) & 0.46695 \\ 
4 & Pavlov \& Brunk (Yandex Labs) & 0.46678 \\ 
5 & Sorokina (Yandex Labs) & 0.46616 \\ 
\end{tabular}
\caption{Final standings of the Yahoo! Learning to Rank Challenge, as presented in the challenge overview paper\cite{Chapelle2011a}}
\label{fig:yahoo_results}
\end{table}
\chapter{Yandex Internet Mathematics competition}
\section{Benchmark characteristics}
\section{Results}
\chapter{LETOR}
\section{Benchmark characteristics}
\section{Results}
\chapter{MSLR-WEB30k}
Contrary to the Yahoo! Learning to Rank Challenge dataset, the MSLR-WEB30k provides detailed feature descriptions. The MSLR-WEB30k dataset however contains no proprietary features but only features that are commonly used in the research community.
\section{Benchmark characteristics}
\section{Results}
